\LARGE Coursework \\ Module Name (CMM...)

### 2018-04-22 submission.tex
added sweave file

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

<<>>=
library(dplyr)
library(rjson)
library(caret)
library(randomForest)
library(ROCR)
library(dummies)

#read in the train and test datasets and combine

df1 <- read.csv('dota_dataset\\dota2Train.csv')
df2 <- read.csv('dota_dataset\\dota2Test.csv')

names(df2) <- names(df1)

#combine the original datasets to a single dataframe
df <- rbind(df1,df2)
rm(df1,df2)
@

@@

<<eval=FALSE>>=

library(xtable)

print(xtable(head(df)))

str(df)

names(df)
@
Let's also check the size of the dataset:
<<>>=
#record number of rows and columns
paste('number of columns =' , ncol(df) , '. number of rows =', nrow(df))
@

Now let's check the class distribution (ie do we have an approximately equal number of team 1 wins as team 2 wins?).
The distribution is indeed close to equal so we do not need to worry about class imbalance later on. It is interesting to note there is some imbalance, the reason for this is not clear but probably has something to do with the manner in which the data was collected.
<<eval=FALSE >>=
#check value distribution of response variable column
table(df[,1])
@

<<eval=FALSE ,echo=FALSE>>=
library(xtable)

print(xtable(table(df[,1])))
@
% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Sun Apr 22 18:14:40 2018
\begin{table}[ht]
\centering
\begin{tabular}{rr}
  \hline
 & V1 \\ 
  \hline
-1 & 48658 \\ 
  1 & 54284 \\ 
   \hline
\end{tabular}
\end{table}

@@

<<>>=
#check for missing values (there are none)
sum(complete.cases(df))==nrow(df)

#check there are equal number of heroes present in each team (hero values for all rows should sum to zero)
sum((rowSums(df[5:ncol(df)]))) == 0
@

As discussed above, some preprocessing is required. First, we convert all numeric columns to factors:
<<>>=
df[sapply(df, is.numeric)] <- lapply(df[sapply(df, is.numeric)], as.factor)
@

The column names are added in two stages. The first four columns are named manually as specified in teh dataset description.\\
The remaining columns represent the individual heros. The column names are extracted from the .json file supplied with the dataset:
<<>>=
#add column names to the first few columns
names(df)[1:4] <- c('won','cluster_id','game_mode','game_type')

#populate the other column names
#load in json file and use it to populate column names
hero_names <- fromJSON(file ="dota_dataset\\heroes.json")

for ( i in c(1:length(hero_names$heroes))){
  names(df)[i+4] <- hero_names$heroes[[i]]$name
}
@

Here we drop columns that are not related to heros (this analysis is concerned only with hero choice so we drop game type and location related columns). 
One column has the same value for every entry. This was noticed during the analysis stage. The column represents a mandatory hero which muct be included in the team. Since it conveys no information it is dropped:
<<>>=
#drop unwanted columns
df <- df%>%
  select(-c(lina, cluster_id , game_mode , game_type))
@

@@

<<warning=FALSE,message=FALSE,eval=FALSE>>=
library(ggplot2)

p <- ggplot(iris, aes(x=Petal.Length, 
                      y = Petal.Width,color=Species) )
p <- p+ geom_point(aes(shape=Species))
p <- p + xlab('Petal Length')
p <- p + ylab('Petal Width')
p <- p + theme_bw()
p

@

@@

<<warning=FALSE,echo=FALSE,fig.height=4.5,out.width=".76\\linewidth">>=
library(ggplot2)

p <- ggplot(iris, aes(x=Petal.Length, 
                      y = Petal.Width,color=Species) )
p <- p+ geom_point(aes(shape=Species))
p <- p + xlab('Petal Length')
p <- p + ylab('Petal Width')
p <- p + theme_bw()
p

@
\caption {Petal Length /Width per species in IRIS set}
\label{fig1}
\end {center}
\end {figure}

\subsection{Build Classifier}
The dataset is now split into training, testing and validation sets. 60\% of the data is used for training with 20\% used for testing and validation respectivley:
<<>>=
set.seed(57)
# Split into train test and validation sets
index <- sample(c(1:3), size = nrow(df), replace = TRUE, prob = c(.6, .2, .2))
df_train <- df[index == 1,]
df_test <- df[index == 2,]
df_valid <- df[index == 3,]
@

@@

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
<<eval=FALSE>>=
num_attributes <- ncol(df_train)
#build a parameter grid
# Random forest
mtry <- as.integer(c(num_attributes * 0.25, num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
nodesize <- c( 3, 5, 20)
ntree <- c(200)

PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
                                         ntree=ntree, stringsAsFactors=F))
@
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table:
<<eval=FALSE>>=
for (i in c(1:nrow(PG))){
  mtry <- PG[i, "mtry"]
  nodesize <- PG[i, "nodesize"]
  ntree <- PG[i, "ntree"]

  temp_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize)
  predictions <- predict(temp_model , df_valid)
  cm<- confusionMatrix(predictions,df_valid$won)
  accuracy <- cm$overall['Accuracy']
  PG[i,'Accuracy'] <- accuracy
  print(i)
}
@

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
<<eval=FALSE>>=
#assess best model on test set
PG <- PG%>%
  arrange(desc(Accuracy))

mtry <- PG[1, "mtry"]
nodesize <- PG[1, "nodesize"]
ntree <- PG[1, "ntree"]
best_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize , importance=T)
predictions <- predict(temp_model , df_valid)
confusionMatrix(predictions,df_valid$won)
@

@@

<<>>=
library(dplyr)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(wordcloud)
library(ggplot2)
library(gridExtra)
library(graph)
library(Rgraphviz)
library(RTextTools)

df <- read.csv("leaveRemainTweets_CW.csv")
@
The 'leave' and 'remain' tweets are seperated and stored in different objects. We also check that we have captured all tweets by seperating by label (ie there a no unlabelled tweets, or any with labels outwith 'leave' or 'remain'):
<<>>=
#seperate dataframes for leave and remain tweets
leave_tweets <- df%>%
  filter(label=="Leave")
remain_tweets <- df%>%
  filter(label=="Remain")

#check we have captured all the tweets
nrow(df)==(nrow(leave_tweets) + nrow(remain_tweets))
@
It is important to ensure the dataset is balanced, ie there are a similar number of leave and remain tweets. This is indeed the case:
<<>>=
nrow(leave_tweets)
nrow(remain_tweets)
@

@@

<<>>=

buildCorpus <- function(someText){

  # build a corpus, and specify the source to be character vectors
  myCorpus <- Corpus(VectorSource(someText))

  myCorpus <- tm_map(myCorpus,
                     content_transformer(function(x) iconv(x, to='UTF-8',sub='byte')))
  myCorpus <- tm_map(myCorpus, content_transformer(tolower))
  # remove punctuation
  myCorpus <- tm_map(myCorpus, removePunctuation)
  # remove numbers
  myCorpus <- tm_map(myCorpus, removeNumbers)
  # remove URLs
  removeURL <- function(x) {
    gsub("http[[:alnum:]]*", "", x)
  }
  myCorpus <- tm_map(myCorpus, removeURL)
  myCorpus <- tm_map(myCorpus, content_transformer(removeURL)) #??
  # add stopwords
  myStopwords <- c(stopwords("english"), "RT","rt","EU","eu","brexit")
  #remove words CONTAINING certain terms
  myCorpus <- tm_map(myCorpus, content_transformer(gsub), pattern = "*vote*|*leave*|*remain*|*stronger*", replacement = "")
  # remove stopwords from corpus
  myCorpus <- tm_map(myCorpus, removeWords, myStopwords)
  #
  myCorpus <- tm_map(myCorpus, stripWhitespace)
  # Return the text corpus
  return(myCorpus)
}
@
In order to explore the tweets, we will construct a document-term matrix. This will be achieved with the following function. The function returns several useful objects:
\begin{itemize}
  \item the document-term matrix
  \item the term-document matrix
  \item a frequency table for individual words (used to make wordclouds)
  \item the text corpus, as produced by the 'buildCorpus' function
\end{itemize}

<<>>=
#function to build term document matrix, along with other useful objects for analysis
make_tdm <- function(text_column,minfreq=1){
  text_column <- iconv(text_column, 'UTF-8', 'ASCII')
  corpus <- buildCorpus(text_column)
  # keep for later
  corpus_copy <- corpus
  # stem words
  corpus <- tm_map(corpus, stemDocument)
  tdm <- TermDocumentMatrix(corpus,control=list(bounds = list(global = c(minfreq,Inf)))) 
  dtm <- DocumentTermMatrix(corpus,control=list(bounds = list(global = c(minfreq,Inf)))) 
  m <- as.matrix(tdm)
  v <- sort(rowSums(m), decreasing = TRUE)
  d <- data.frame(word = names(v), freq = v)
  return(list(corpus=corpus,freq_table=d,tdm=tdm , dtm=dtm))
}
@
As the 'maketdm' function outputs a word frequency table, we can use it to produce word clouds for the leave and remain tweets. To avoid repeating tasks, the process for making and plotting wordclouds is defined in dedicated functions.

<<>>=
#make corpuses and tdms from the tweets
all_tweets <- make_tdm(df$text)
remain <- make_tdm(remain_tweets$text)
leave <- make_tdm(leave_tweets$text)

#function to make wordclouds
make_wordcloud <- function(freq_tab){
wordcloud(words = freq_tab$word, freq = freq_tab$freq, min.freq = 5,max.words=2000, random.order=FALSE, rot.per=0.2,colors=brewer.pal(8, "Dark2"))
}
@
\begin{figure}[H]
\begin{center}

<<fig=TRUE>>=
#make wordclouds from the frequency tables
make_wordcloud(remain$freq_tab)
@

@@

\begin{figure}[H]
\begin{center}
<<fig=TRUE>>=
make_wordcloud(leave$freq_tab)
@
\caption {Wordclouds for the leave tweets}
\label{fig11}
\end {center}
\end {figure}

In addition to wordclouds, we can plot the most common words for each class of tweet. This is achieve with the function below:
<<>>=
#function to plot wordclouds
plot_wordcount <- function(freq_tab,title_text){
  ggplot(head(freq_tab,20), aes(x=word,y=freq))+
    geom_bar(stat="identity")+
    labs(title=title_text)+
    theme(axis.text.x = element_text(angle = 30, hjust = 1))
}
a<-plot_wordcount(all_tweets$freq_table,"most common words for all tweets")
b<-plot_wordcount(remain$freq_table,"most common words for remain tweets")
c<-plot_wordcount(leave$freq_table,"most common words for leave tweets")

@

\begin{figure}[H]
\begin{center}
<<fig=TRUE>>=
grid.arrange(a,b,c, nrow = 3)
@
\caption {Wordcounts for the tweets}
\label{fig10}
\end {center}
\end {figure}

>>>>

\usepackage{Sweave}
\begin{document}
\input{submission-concordance}

@@

\begin{Schunk}
\begin{Sinput}
> library(dplyr)
> library(rjson)
> library(caret)
> library(randomForest)
> library(ROCR)
> library(dummies)
> #read in the train and test datasets and combine 
> 
> df1 <- read.csv('dota_dataset\\dota2Train.csv')
> df2 <- read.csv('dota_dataset\\dota2Test.csv')
> names(df2) <- names(df1)
> #combine the original datasets to a single dataframe
> df <- rbind(df1,df2)
> rm(df1,df2)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> library(xtable)
> print(xtable(head(df)))
> str(df)
> names(df)
\end{Sinput}
\end{Schunk}
Let's also check the size of the dataset:
\begin{Schunk}
\begin{Sinput}
> #record number of rows and columns
> paste('number of columns =' , ncol(df) , '. number of rows =', nrow(df))
\end{Sinput}
\begin{Soutput}
[1] "number of columns = 117 . number of rows = 102942"
\end{Soutput}
\end{Schunk}

Now let's check the class distribution (ie do we have an approximately equal number of team 1 wins as team 2 wins?).
The distribution is indeed close to equal so we do not need to worry about class imbalance later on. It is interesting to note there is some imbalance, the reason for this is not clear but probably has something to do with the manner in which the data was collected.
\begin{Schunk}
\begin{Sinput}
> #check value distribution of response variable column
> table(df[,1])
\end{Sinput}
\end{Schunk}

% latex table generated in R 3.4.3 by xtable 1.8-2 package
% Sun Apr 22 18:14:40 2018
\begin{table}[ht]
\centering
\begin{tabular}{rr}
  \hline
 & V1 \\ 
  \hline
-1 & 48658 \\ 
  1 & 54284 \\ 
   \hline
\end{tabular}
\end{table}

@@

\begin{Schunk}
\begin{Sinput}
> #check for missing values (there are none)
> sum(complete.cases(df))==nrow(df)
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\begin{Sinput}
> #check there are equal number of heroes present in each team (hero values for all rows should sum to zero)
> sum((rowSums(df[5:ncol(df)]))) == 0
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}

As discussed above, some preprocessing is required. First, we convert all numeric columns to factors:
\begin{Schunk}
\begin{Sinput}
> df[sapply(df, is.numeric)] <- lapply(df[sapply(df, is.numeric)], as.factor)
\end{Sinput}
\end{Schunk}

The column names are added in two stages. The first four columns are named manually as specified in teh dataset description.\\
The remaining columns represent the individual heros. The column names are extracted from the .json file supplied with the dataset:
\begin{Schunk}
\begin{Sinput}
> #add column names to the first few columns
> names(df)[1:4] <- c('won','cluster_id','game_mode','game_type')
> #populate the other column names
> #load in json file and use it to populate column names
> hero_names <- fromJSON(file ="dota_dataset\\heroes.json")
> for ( i in c(1:length(hero_names$heroes))){
+   names(df)[i+4] <- hero_names$heroes[[i]]$name
+ }
\end{Sinput}
\end{Schunk}

Here we drop columns that are not related to heros (this analysis is concerned only with hero choice so we drop game type and location related columns). 
One column has the same value for every entry. This was noticed during the analysis stage. The column represents a mandatory hero which muct be included in the team. Since it conveys no information it is dropped:
\begin{Schunk}
\begin{Sinput}
> #drop unwanted columns
> df <- df%>%
+   select(-c(lina, cluster_id , game_mode , game_type))
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> library(ggplot2)
> p <- ggplot(iris, aes(x=Petal.Length, 
+                       y = Petal.Width,color=Species) )
> p <- p+ geom_point(aes(shape=Species))
> p <- p + xlab('Petal Length')
> p <- p + ylab('Petal Width')
> p <- p + theme_bw()
> p
> 
\end{Sinput}
\end{Schunk}

@@

\caption {Petal Length /Width per species in IRIS set}
\label{fig1}
\end {center}
\end {figure}

\subsection{Build Classifier}
The dataset is now split into training, testing and validation sets. 60\% of the data is used for training with 20\% used for testing and validation respectivley:
\begin{Schunk}
\begin{Sinput}
> set.seed(57)
> # Split into train test and validation sets
> index <- sample(c(1:3), size = nrow(df), replace = TRUE, prob = c(.6, .2, .2))
> df_train <- df[index == 1,]
> df_test <- df[index == 2,]
> df_valid <- df[index == 3,]
\end{Sinput}
\end{Schunk}

@@

Here, a parameter grid is defined and stored as a dataframe to be accessed as each candidate model is trained
\begin{Schunk}
\begin{Sinput}
> num_attributes <- ncol(df_train)
> #build a parameter grid
> # Random forest
> mtry <- as.integer(c(num_attributes * 0.25, num_attributes / 3, num_attributes * 0.5, num_attributes * 0.8))
> nodesize <- c( 3, 5, 20)
> ntree <- c(200)
> PG<- as.data.frame(expand.grid(mtry=mtry, nodesize=nodesize,
+                                          ntree=ntree, stringsAsFactors=F))
\end{Sinput}
\end{Schunk}
Now, we train up a random forest on the training set for each combination of parameters in the parameter grid. \\
For each combination of parameters, the resulting model is tested on the evaluation set and the accuracy calculated.
The resulting accuracy from each parameter combination is saved in the 'Accuracy' column of the parameter grid table:
\begin{Schunk}
\begin{Sinput}
> for (i in c(1:nrow(PG))){
+   mtry <- PG[i, "mtry"]
+   nodesize <- PG[i, "nodesize"]
+   ntree <- PG[i, "ntree"]
+ 
+   temp_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize)
+   predictions <- predict(temp_model , df_valid)
+   cm<- confusionMatrix(predictions,df_valid$won)
+   accuracy <- cm$overall['Accuracy']
+   PG[i,'Accuracy'] <- accuracy
+   print(i)
+ }
\end{Sinput}
\end{Schunk}

The parameters which produced the best model are selected and that model is evaluated on the testing set to give a final accuracy for the random forest classifier.
\begin{Schunk}
\begin{Sinput}
> #assess best model on test set
> PG <- PG%>%
+   arrange(desc(Accuracy))
> mtry <- PG[1, "mtry"]
> nodesize <- PG[1, "nodesize"]
> ntree <- PG[1, "ntree"]
> best_model <- randomForest(formula(df_train) , data=df_train, mtry=mtry, ntree=ntree, nodesize=nodesize , importance=T)
> predictions <- predict(temp_model , df_valid)
> confusionMatrix(predictions,df_valid$won)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> library(dplyr)
> library(tm)
> library(SnowballC)
> library(RColorBrewer)
> library(wordcloud)
> library(ggplot2)
> library(gridExtra)
> library(graph)
> library(Rgraphviz)
> library(RTextTools)
> df <- read.csv("leaveRemainTweets_CW.csv")
\end{Sinput}
\end{Schunk}
The 'leave' and 'remain' tweets are seperated and stored in different objects. We also check that we have captured all tweets by seperating by label (ie there a no unlabelled tweets, or any with labels outwith 'leave' or 'remain'):
\begin{Schunk}
\begin{Sinput}
> #seperate dataframes for leave and remain tweets
> leave_tweets <- df%>%
+   filter(label=="Leave")
> remain_tweets <- df%>%
+   filter(label=="Remain")
> #check we have captured all the tweets
> nrow(df)==(nrow(leave_tweets) + nrow(remain_tweets))
\end{Sinput}
\begin{Soutput}
[1] TRUE
\end{Soutput}
\end{Schunk}
It is important to ensure the dataset is balanced, ie there are a similar number of leave and remain tweets. This is indeed the case:
\begin{Schunk}
\begin{Sinput}
> nrow(leave_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1254
\end{Soutput}
\begin{Sinput}
> nrow(remain_tweets)
\end{Sinput}
\begin{Soutput}
[1] 1029
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> buildCorpus <- function(someText){
+   
+   # build a corpus, and specify the source to be character vectors
+   myCorpus <- Corpus(VectorSource(someText))
+ 
+   myCorpus <- tm_map(myCorpus,
+                      content_transformer(function(x) iconv(x, to='UTF-8',sub='byte')))
+   myCorpus <- tm_map(myCorpus, content_transformer(tolower))
+   # remove punctuation
+   myCorpus <- tm_map(myCorpus, removePunctuation)
+   # remove numbers
+   myCorpus <- tm_map(myCorpus, removeNumbers)
+   # remove URLs
+   removeURL <- function(x) {
+     gsub("http[[:alnum:]]*", "", x)
+   }
+   myCorpus <- tm_map(myCorpus, removeURL)
+   myCorpus <- tm_map(myCorpus, content_transformer(removeURL)) #??
+   # add stopwords
+   myStopwords <- c(stopwords("english"), "RT","rt","EU","eu","brexit")
+   #remove words CONTAINING certain terms
+   myCorpus <- tm_map(myCorpus, content_transformer(gsub), pattern = "*vote*|*leave*|*remain*|*stronger*", replacement = "")
+   # remove stopwords from corpus
+   myCorpus <- tm_map(myCorpus, removeWords, myStopwords)
+   #
+   myCorpus <- tm_map(myCorpus, stripWhitespace)
+   # Return the text corpus
+   return(myCorpus)
+ }
\end{Sinput}
\end{Schunk}
In order to explore the tweets, we will construct a document-term matrix. This will be achieved with the following function. The function returns several useful objects:
\begin{itemize}
  \item the document-term matrix
  \item the term-document matrix
  \item a frequency table for individual words (used to make wordclouds)
  \item the text corpus, as produced by the 'buildCorpus' function
\end{itemize}

\begin{Schunk}
\begin{Sinput}
> #function to build term document matrix, along with other useful objects for analysis
> make_tdm <- function(text_column,minfreq=1){
+   text_column <- iconv(text_column, 'UTF-8', 'ASCII')
+   corpus <- buildCorpus(text_column)
+   # keep for later
+   corpus_copy <- corpus
+   # stem words
+   corpus <- tm_map(corpus, stemDocument)
+   tdm <- TermDocumentMatrix(corpus,control=list(bounds = list(global = c(minfreq,Inf)))) 
+   dtm <- DocumentTermMatrix(corpus,control=list(bounds = list(global = c(minfreq,Inf)))) 
+   m <- as.matrix(tdm)
+   v <- sort(rowSums(m), decreasing = TRUE)
+   d <- data.frame(word = names(v), freq = v)
+   return(list(corpus=corpus,freq_table=d,tdm=tdm , dtm=dtm))
+ }
\end{Sinput}
\end{Schunk}
As the 'maketdm' function outputs a word frequency table, we can use it to produce word clouds for the leave and remain tweets. To avoid repeating tasks, the process for making and plotting wordclouds is defined in dedicated functions.

\begin{Schunk}
\begin{Sinput}
> #make corpuses and tdms from the tweets
> all_tweets <- make_tdm(df$text)
> remain <- make_tdm(remain_tweets$text)
> leave <- make_tdm(leave_tweets$text)
> #function to make wordclouds
> make_wordcloud <- function(freq_tab){
+ wordcloud(words = freq_tab$word, freq = freq_tab$freq, min.freq = 5,max.words=2000, random.order=FALSE, rot.per=0.2,colors=brewer.pal(8, "Dark2"))
+ }
\end{Sinput}
\end{Schunk}
\begin{figure}[H]
\begin{center}

\begin{Schunk}
\begin{Sinput}
> #make wordclouds from the frequency tables
> make_wordcloud(remain$freq_tab)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-022}

@@

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> make_wordcloud(leave$freq_tab)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-023}
\caption {Wordclouds for the leave tweets}
\label{fig11}
\end {center}
\end {figure}

In addition to wordclouds, we can plot the most common words for each class of tweet. This is achieve with the function below:
\begin{Schunk}
\begin{Sinput}
> #function to plot wordclouds
> plot_wordcount <- function(freq_tab,title_text){
+   ggplot(head(freq_tab,20), aes(x=word,y=freq))+
+     geom_bar(stat="identity")+
+     labs(title=title_text)+
+     theme(axis.text.x = element_text(angle = 30, hjust = 1))
+ }
> a<-plot_wordcount(all_tweets$freq_table,"most common words for all tweets")
> b<-plot_wordcount(remain$freq_table,"most common words for remain tweets")
> c<-plot_wordcount(leave$freq_table,"most common words for leave tweets")
> 
> 
> 
\end{Sinput}
\end{Schunk}

\begin{figure}[H]
\begin{center}
\begin{Schunk}
\begin{Sinput}
> grid.arrange(a,b,c, nrow = 3)
\end{Sinput}
\end{Schunk}
\includegraphics{submission-025}
\caption {Wordcounts for the tweets}
\label{fig10}
\end {center}
\end {figure}
